Some usefull words/expressions/sentences

### 2018-07-08 paper/main.tex
update of the main acknowledgement

\thesistitle{The timing of Carbonhydrate intake in the NDNS 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\begin{itemize}
\item This work was done wholly or mainly while in candidature for a research degree at this University.
\item Where any part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution, this has been clearly stated.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

@@

@@

\noindent\enquote{\itshape Thanks to my solid academic training, today I can write hundreds of words on virtually any topic without possessing a shred of information, which is how I got a good job in journalism.}\bigbreak

\hfill Dave Barry

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
The acknowledgments and the people to thank go here, don't forget to include your project advisor\ldots
\end{acknowledgements}

>>>>

\thesistitle{The timing of carbohydrate intake in UK adults, using the National Dietary and Nutrition Survey (NDNS) 2008-2014 programme} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Professor Luigi \textsc{Palla}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{MSc in Medical Statistics} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Chaochen \textsc{Wang}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

@@

\begin{itemize}
\item This work was done wholly or mainly while in candidature for a MSc degree on Medical Statistics at this University.
\item No part of this thesis has previously been submitted for a degree or any other qualification at this University or any other institution.
\item Where I have consulted the published work of others, this is always clearly attributed.
\item Where I have quoted from the work of others, the source is always given. With the exception of such quotations, this thesis is entirely my own work.
\item I have acknowledged all main sources of help.
\item Where the thesis is based on work done by myself jointly with others, I have made clear exactly what was done by others and what I have contributed myself.\\
\end{itemize}

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr. Suzana Almoosawi for her invaluable nutritional academic insight, and suggestions. \\

Thanks to Raoul Mansukhani, for sharing his previous work and thoughts on the analyses, methodology in helpful discussions.	 \\

I would like to thank the team of the National Dietary and Nutrition Survey (NDNS) who have made their data available to the public for academic study. \\

I would like to thank all of the teachers, lecturers, staffs, and fellow course mates in the Department of Medical Statistics for providing their wonderful teaching techniques, sharing their excellent ideas that made this year such fruitful and enjoyable.\\

I also want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\

\end{acknowledgements}

@@

\noindent\enquote{\itshape All models are wrong, but some are useful.}\bigbreak

\hfill George E. P. Box

@@

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The National Dietary and Nutrition Survey (NDNS) database of detailed four-day food diaries was used to \dots
\end{abstract}
